---
title: "Metajam Demo"
author: "Julien Brun, NCEAS"
date: "NCEAS roundtable, 11/14/2018"
output: 
  html_document:
    theme: "spacelab"
    df_print: "paged"
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```


# Single dataset

Data Package on KNB: https://knb.ecoinformatics.org/view/doi:10.5063/F1CJ8BPH

```{r single download, eval=FALSE}
library(metajam)

dataset_url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3A7fc6f6db-c5ea-426a-a743-1f2edafb43b8"
data_path <- "~/Desktop"

prod_path <- download_d1_data(data_url = dataset_url, path = data_path)
```

```{r single read}
hh_lang <- read_d1_files(folder_path  = prod_path)
```

```{r german in alaska}
library(tidyverse)

german_sp <- hh_lang$data %>% 
  group_by(Year) %>% 
  summarize(n_german = sum(german))

                                           
plot(german_sp)                                              
                                               
```


# Single dataset - with header

Data Package on ADC: https://doi.org/10.18739/A2ZX05

```{r single download header}
library(metajam)

dataset_url <- "urn%3Auuid%3Aec05ab95-844c-4cf0-95b0-40e02ba44f63"
data_path <- "~/Desktop"

prod_path <- download_d1_data(data_url = dataset_url, path = data_path)
```


```{r read data header}
data_transect <- read_d1_files(prod_path)
```

```{r}
View(data_transect$data)
```

Does not look right!!


There is a header!! since `read_d1_files` use `readr::read_csv` by default we can pass all the options this function has:

```{r read data header with param, }
data_transect <- read_d1_files(prod_path, skip=7)

View(data_transect$data)
```
```{r}
View(data_transect$data)
```

# Changing the function to read files - Excel

Data package on KNB: https://doi.org/10.5063/F19W0CQ5

```{r single download xlsx, eval=FALSE}
library(metajam)

dataset_url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Ab04cd4ce-ee5f-416a-89d4-83ac80180a26"
data_path <- "~/Desktop"

yield_path <- download_d1_data(data_url = dataset_url, path = data_path)

# View(yield_data$data)
```

## Read the data 

```{r read xlsx}
library(readxl)

yield_data <- read_d1_files(yield_path, "read_excel")

```

# Check version

```{r check version}
check_version("doi:10.18739/A2HF7Z", formatType = "metadata")
```

# Not limited to tabular data

Data package on KNB: https://doi.org/10.5063/F1KD1VVS

```{r geospatial}

# download_d1_data("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/karakoenig.31.1", "~/Desktop")

# Read the geojson
nm_wells <- geojsonio::geojson_read("~/Desktop/brun.34.23__nmwells/nmwellsNA.json", what="sp")

# Map it
leaflet::leaflet(nm_wells) %>%
  setView(-98, 40, zoom = 4)
  leaflet::addTiles() %>% 
  leaflet::addCircleMarkers()
  
# Still works to load metadata
read_d1_files("~/Desktop/brun.34.23__nmwells")
```


# Batch download datasets

https://nceas.github.io/metajam/articles/dataset-batch-processing.html


# Download the whole package

https://nceas.github.io/metajam/articles/package-download.html

